Hierarchical time series forecasting in Emergency Medical Services

### 2022-11-16 manuscript/main.qmd
Back to pdflatex

bibliography: bibliography.bib
execute:
  echo: false
  message: false
  warning: false
pdf-engine: latexmk
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Annals of Emergency Medicine
      formatting: preprint
      model: 3p
      cite-style: authoryear
---

>>>>

bibliography: bibliography.bib
execute:
  echo: false
  message: false
  warning: false
pdf-engine: pdflatex
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Annals of Emergency Medicine
      formatting: preprint
      model: 3p
      cite-style: authoryear
---
